---
title: "Lompoc Edible Trail Project Dashboard"
format: 
  html:
    code-fold: true
    theme: cosmo
runtime: shiny
---

# Welcome

Welcome to the interactive dashboard for the Lompoc Edible Trail Project. Explore our timeline, maps, and latest updates!

# Project Timeline

```{r}
library(timevis)

events <- data.frame(
  id = 1:10,
  content = c(
    "Community Intro & Feedback",
    "Advisory Committee Formation",
    "Site Selection",
    "Fundraising",
    "Design & Site Prep",
    "Planting & Build-Out",
    "Community Programming",
    "Maintenance & Stewardship",
    "Monitoring & Feedback",
    "Expansion Planning"
  ),
  start = c("2024-07-01", "2024-09-01", "2024-11-01", "2025-01-01", 
            "2025-03-01", "2025-05-01", "2025-07-01", "2025-09-01", 
            "2025-11-01", "2026-01-01"),
  end = c("2025-02-28", "2024-10-31", "2024-12-31", "2025-02-28", 
          "2025-06-30", "2025-08-31", "2025-10-31", "2026-02-28", 
          "2026-04-30", "2026-06-30")
)

timevis(events)
```

# Map of Trail Segments

```{r}

library(leaflet)

leaflet() %>%
  addTiles() %>%
  addMarkers(lng = -120.464, lat = 34.639, popup = "Lompoc Riverbend Trail Start") %>%
  addCircleMarkers(lng = c(-120.464, -120.459), lat = c(34.639, 34.645),
                   label = c("Trail Segment 1", "Pilot Edible Segment"))

```

# Latest Updates

July 2024: Community meetings ongoing. Join us at Old Town Fridays!
August 2024: Advisory Committee formed. Seeking volunteers for planting days.

# Get Involved


---

## 4. Hosting & Sharing

- Deploy on **shinyapps.io** (free tier available) or your own server.
- Or publish as a **Quarto website** on GitHub Pages with embedded shinylive apps for lightweight interactivity.
- Share link via social media, newsletters, city websites, and community centers.

---

## 5. Next Steps from Here

- Would you want help with actual R/Quarto code for the timeline or map?  
- Interested in a fully interactive Shiny app example?  
- Do you have geo data (coordinates) for the trail and key sites?  
- Would you like templates for updating the dashboard with new progress info?

---

Feel free to share more details or priorities, and I can help you build a customized, practical dashboard to engage your community effectively!

