---
title: "Lompoc Edible Trail Proposal Dashboard"
format: html
runtime: shiny
css: styles.css
---


```{r echo = FALSE, message=FALSE}

library(shiny)
library(leaflet)
library(timevis)
```

<style> /* Your custom CSS */ body { font-family: 'Helvetica Neue', Helvetica, Arial, sans-serif; background: #f9f9f9; color: #333; line-height: 1.6; } h1, h2, h3 { color: #2c3e50; font-weight: 700; margin-top: 1.5em; margin-bottom: 0.5em; } .timevis-event { border-radius: 8px !important; box-shadow: 0 2px 6px rgba(0,0,0,0.15); font-weight: 600; } .phase-1 { background-color: #4a90e2 !important; color: white !important; font-size: 1.1em !important; } .phase-2 { background-color: #f5a623 !important; color: white !important; font-size: 1.1em !important; } .phase-3 { background-color: #7ed321 !important; color: white !important; font-size: 1.1em !important; } .leaflet-container { border-radius: 10px; box-shadow: 0 2px 8px rgba(0,0,0,0.2); height: 450px !important; } .summary-highlight { background: #fff; padding: 15px 20px; border-radius: 8px; box-shadow: 0 1px 5px rgba(0,0,0,0.1); margin-bottom: 1em; } .get-involved { margin-top: 30px; background: #fff; padding: 20px; border-radius: 8px; text-align: center; box-shadow: 0 2px 6px rgba(0,0,0,0.15); font-size: 1.1em; font-weight: 600; color: #2c3e50; } </style>

## Welcome to the ***Lompoc Edible Trail Project*** info page! This site was created to stay transparent. You will be able to check out the timeline, track progress, stay informed, or get engaged.

# Proposed Solution

<div style="max-height:300px; overflow-y:auto; padding: 10px; border: 1px solid #ccc;"> To address limited food access and fragmented green infrastructure, this project proposes a community-driven edible and ecological trail system. It will transform underutilized public spaces into green corridors providing fresh food, environmental benefits, and social cohesion.<br><br> The trail will include fruit & nut trees, native plants, shaded paths, educational signage, and produce-sharing kiosks — creating multifunctional spaces blending ecology and food production. </div>

# Community Engagement & Co-Design

<div style="max-height:300px; overflow-y:auto; padding: 10px; border: 1px solid #ccc;"> Sustained community involvement is key, with workshops, advisory committees, and participatory design. The project embraces local narratives, bilingual signage, and culturally relevant elements to foster trust and long-term stewardship. </div>


# Proposed Timeline


```{r, echo=FALSE}

library(timevis)

phase_colors <- c(
  "Phase 1" = "#5dade2",
  "Phase 2" = "#58d68d",
  "Phase 3" = "#f5b041"
)

tasks <- data.frame(
  id = 1:9,
  content = c(
    "Community Intro & Feedback",
    "Advisory Committee Formation",
    "Site Selection",
    "Fundraising",
    "Installation",
    "Community Planting",
    "Programming Launch",
    "Maintenance",
    "Monitoring & Expansion"
  ),
  start = c(
    "2025-10-01", "2025-12-01", "2026-01-01",
    "2026-03-01", "2026-06-01", "2026-07-01",
    "2026-09-01", "2026-12-01", "2027-03-01"
  ),
  end = c(
    "2025-11-30", "2025-12-31", "2026-02-28",
    "2026-05-31", "2026-07-31", "2026-08-31",
    "2026-11-30", "2027-05-31", "2027-09-30"
  ),
  group = c(
    "Phase 1", "Phase 1", "Phase 1",
    "Phase 1", "Phase 2", "Phase 2",
    "Phase 2", "Phase 3", "Phase 3"
  ),
  stringsAsFactors = FALSE
)

timevis(tasks)


```



# Trail Map


```{r, echo=FALSE}

library(leaflet)
leaflet() %>%
  addTiles() %>%
  addMarkers(lng = -120.444229, lat = 34.666243, popup = "Lompoc Riverbend Trail Start") %>%
  addMarkers(lng = -120.435763, lat = 34.647437, popup = "Lompoc Riverbend Trail End") %>%
  addCircleMarkers(
    lng = c(-120.442545, -120.442917),
    lat = c(34.660277, 34.660787),
    label = c("Proposed Segment 1", "Proposed Segment 2"),
    color = c("red4", "yellow3")
  )



```

# Summary Highlights

<div class="summary-highlight"> <ul> <li><strong>Community-Driven:</strong> Phases start with strong community engagement and advisory committees.</li> <li><strong>Fundraising & Partnerships:</strong> Early and ongoing resource development supports installation.</li> <li><strong>Installation:</strong> Pilot trail segment built with local volunteers and sustainable materials.</li> <li><strong>Stewardship & Expansion:</strong> Community stewardship teams formed, with monitoring and plans to grow.</li> </ul> </div>

# Get Involved

<div class="get-involved"> Stay updated and participate! Contact us at <a href="mailto:lompoctrail@example.org">lompoctrail@example.org</a> </div> 

```{r, echo=FALSE}
shinyApp(ui, server)

```

